Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-21 main.tex
Updates from Overleaf

\section{LSBG search in HSC PDR2}
Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. For those who do not want to be bothered by technical details, we outline the major steps below:
\begin{enumerate}
    \item Source Detection (Sec. \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (Sec. \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}. We use \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement errors (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}

@@

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size.

Compare with vdb17, carlsten22, smudges21/22, tanoglidis21.

Our high completeness demonstrates the power of HSC images on LSBG studies.

\jiaxuan{Also compare our completeness with other surveys.}

>>>>

\section{LSBG search in HSC PDR2}
Continuing the work in \citet{Greco2018} (hereafter \citetalias{Greco2018}), we conduct a systematic search for low surface brightness galaxies in the PDR2 data, which covers $\sim 1.5$ of the sky area in \citetalias{Greco2018}. The schematic of the searching method in this paper remains similar to that in \citetalias{Greco2018}, but we do improve the searching completeness and purity by adding several new steps, which are highlighted in this section. For those who do not want to be bothered by technical details, we outline the major steps below:
\begin{enumerate}
    \item Source Detection (Sec. \ref{sec:detection}): we run \code{Source Extractor} on the coadd images after removing bright extended sources. Then we apply an initial size and color cut based on the output catalog. 
    \item Deblending (Sec. \ref{sec:deblending}): we remove false positives that are not likely to be LSBGs by running \code{scarlet}. We use \code{scarlet} models to define color-size-morphology-surface brightness cuts. This step removes roughly 97\% of false positives.
    \item Modeling (Sec. \ref{sec:modeling}): we fit a parametric model to the LSBGs to estimate their structural parameters. 
    \item Completeness and measurement uncertainties (Sec. \ref{sec:comp_meas}) are characterized by injecting mock \sersic{} galaxies into images. 
\end{enumerate}

@@

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops as we go to fainter surface brightness and smaller size. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$.

% As noted in Paper II, our ability to estimate uncertainties and completeness is limited by the differences between our smooth Sérsic models and real UDGs, some of which may have complex morphologies. Nonetheless, they do provide baseline estimates of these parameters, which may be augmented in the future by comparing our results to other surveys using different observational and analytic strategies.

% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.

We compare our completeness with that of other LSBG searches. Our completeness is most similar to \citetalias{Greco2018}, where they also reach $\sim 50\%$ at $\sbeff \approx 27.0\ \sbunit$ and $3\arcsec < r_e < 12\arcsec$ \citep{Kado-Fong2021,Greene2022}, but their completeness decreases more as increasing size. \citet{CarlstenELVES2022} use a similar searching algorithm to \citetalias{Greco2018} and ours and reach a completeness of $\sim 50\%$ at $\mu_0(g)\approx 26.5\ \sbunit$ or equivalently $\sbeff = 27.5\ \sbunit$. \citet{vdBurg2017} searched LSBGs from the ESO Kilo-Degree Survey data and achieved $\sim 50\%$ completeness at $\sbeffr\approx 26.0\ \sbunit$ or equivalently $\sbeff \approx 26.6\ \sbunit$. \citet{Zaritsky2021} focus on searching LSBGs in SDSS Stripe82 region using the Dark Energy Camera Legacy Survey (DECaLS, \citealt{Dey2019}) survey and reach $\sim 25\%$ completeness at $\mu_{0}(g) \approx 25.5\ \sbunit$ or equivalently $\sbeff \approx 26.5\ \sbunit$. Their low completeness might be explained by the fact that they remove a large fraction of the sky covered by the Galactic dust. \citet{Tanoglidis2021} conducted LSBG search using the Dark Energy Survey (DES, \citealt{Abbot2018}) data but did not provide systematic analysis on completeness using mock galaxies. They compare their catalog with the deeper observations in the Fornax cluster and conclude an overall completeness of $\sim 40\%$. \citet{Kado-Fong2021} estimate the completeness of \citet{Tanoglidis2021} by comparing with \citetalias{Greco2018} and find a completeness similar to \citetalias{Greco2018} at $\sbeff = 25.5\ \sbunit$ but much smaller completeness above $\sbeff > 26.5\ \sbunit$. In summary, our search achieves an overall high completeness compared with other works, and we demonstrate the great potential of HSC data on LSBG studies.
